---
title: "Histogram Analysis Report"
author: "Your Name"
output: html_document
---

## Introduction

This report demonstrates how to generate histograms using different datasets and vectors in R.

## Histogram from Custom Vector

```{r}
v <- c(9,13,21,8,36,22,12,41,31,33,19)

hist(v,
     xlab = "Weight",
     col = "green",
     border = "blue")
```

This histogram shows the distribution of weights stored in a custom vector.

---

## Histogram using mtcars Dataset

```{r}
data(mtcars)

hist(mtcars$mpg,
     main = "Histogram of Miles Per Gallon",
     xlab = "Miles Per Gallon (MPG)",
     col = "yellow",
     border = "black")
```

The histogram above shows the MPG distribution from the mtcars dataset.

---

## Histogram with Custom Axis Limits

```{r}
v <- c(9,13,21,8,36,22,12,41,31,33,19)

hist(v,
     xlab = "Weight",
     col = "blue",
     border = "black",
     xlim = c(0,40),
     ylim = c(0,5),
     breaks = 5)
```

This example demonstrates setting custom axis limits and number of bins.

---

## Histogram using cars Dataset

```{r}
data(cars)

hist(cars$speed,
     main = "Histogram of Car Speed",
     xlab = "Speed",
     col = "yellow",
     border = "black")
```

This histogram shows the distribution of car speeds.